Using Cell Phone Keyboards is (\NP) Hard

### 2010-01-21 article.tex
Small changes.  Looking good!

\begin{figure}
\includegraphics[width=2in]{phonekeys.jpg}
\caption{A cell phone keyboard}
\label{keypic}
\end{figure}

@@

There are two cases for layer $T_i$.  In the first case, $T_i < k$, and we may
remove any element from a later layer and create a strictly better layout.  In
the second case, there is some letter $a$ such that $a \in T_i$ and $a \not\in
S_i$.  We choose the least-frequent such $a$.  Because the greedy layout
algorithm creates layers in order of frequency, we know that the frequency of
$a$ is less than that of some letter $b$ in layer $T_j$, $j>i$.  Therefore, by
creating a new layout with $a$ and $b$ swapped between $T_i$ and $T_j$, we have
strictly decreased the number of button presses.  Therefore, in both cases,
$T$ was not an optimal layout, and we have reached our contradiction.
\end{proof}

@@

By an argument symmetric to the proof of Theorem~\ref{basicthm}, we find that
the optimal layout in this new scheme is to place the letters of a given key in
sorted order.  Thus, the keyboard layout changes to $2\to[acb], 3\to[edf],
4\to[ihg], 5\to[lkj], 6\to[onm], 7\to[srpq], 8\to[tuv], 9\to[wyxz]$ and
requires 678,547,463 button presses to enter the whole corpus.  This represents
a $28.43\%$ savings, but has the added benefit that it does not change which
key is mapped to which set of letters.  This makes it \newword{legacy
preserving}, as creating a keyboard with this layout will not invalidate such
advertising gems as 1-800-FLOWERS.  Thus, we can speed up users by $28.43\%$
(neglecting inter-letter pauses) and not undermine 50 years of advertising.
This layout represents perhaps the most plausible layout yet\footnote{The
described layout is the only legacy preserving layout in this paper, and
therefore should be considered the most practical suggestion.  It also has the
added benefit of not angering any of the organizations behind the numbers
1-800-FLOWERS, 1-800-THRIFTY, and 1-800-MARINES}.  After setting up this
baseline for the easy problem, we turn our attention to optimizing cellphone
keyboards for predictive input methods.

@@

Now we prove that given a $k$-unique-path coloring of $G'$ and $P$ we can create a $k$-coloring of $G$.

\end{proof}

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[width=2in]{phonekeys.jpg}
\end{center}
\caption{A cell phone keyboard}
\label{keypic}
\end{figure}

@@

There are two cases for layer $T_i$.  In the first case, $|T_i| < k$, and we may
remove any element from a later layer place it in layer $T_i$ and create a strictly better layout.  In
the second case, there is some letter $a$ such that $a \in T_i$ and $a \not\in
S_i$.  We choose the least-frequent such $a$.  Because the greedy layout
algorithm creates layers in order of frequency, we know that the frequency of
$a$ is less than that of some letter $b$ in layer $T_j$, $j>i$.  Therefore, by
creating a new layout with $a$ and $b$ swapped between $T_i$ and $T_j$, we have
strictly decreased the number of button presses.  Therefore, in both cases,
$T$ was not an optimal layout, and we have reached our contradiction.
\qed
\end{proof}

@@

By an argument symmetric to the proof of Theorem~\ref{basicthm}, we find that
the optimal layout in this new scheme is to place the letters of a given key in
sorted order, according to frequency.  Thus, the keyboard layout changes to
$2\to[acb], 3\to[edf], 4\to[ihg], 5\to[lkj], 6\to[onm], 7\to[srpq], 8\to[tuv],
9\to[wyxz]$ and requires 678,547,463 button presses to enter the whole corpus.
This represents a $28.43\%$ savings, but has the added benefit that it does not
change which key is mapped to which set of letters.  This makes it
\newword{legacy preserving}, as creating a keyboard with this layout will not
invalidate such advertising gems as 1-800-FLOWERS.  Thus, we can speed up users
by $28.43\%$ (neglecting inter-letter pauses) and not undermine 50 years of
advertising.  This layout represents perhaps the most plausible layout
yet\footnote{The described layout is the only legacy preserving layout in this
paper, and therefore should be considered the most practical suggestion.  It
also has the added benefit of not angering any of the organizations behind the
numbers 1-800-FLOWERS, 1-800-THRIFTY, and 1-800-MARINES}.  After setting up
this baseline for the easy problem, we turn our attention to optimizing
cellphone keyboards for predictive input methods.

@@

Now we prove that given a $k$-unique-path coloring of $G'$ and $P$ we can create a $k$-coloring of $G$.
\qed
\end{proof}
